
\chapter{Introduction}
    \section{Purpose}
        \paragraph{}
The Bid Emission and Exchange Protocol is a protocol for a distributed
bid systems. It enables users using the client to bid for objects among a list. This
protocol is referred to as the BEEP/0.1a.

    \section{Requirements}
        \paragraph{}
The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT",
"SHOULD", "SHOULD NOT", "RECOMMENDED", "MAY", and "OPTIONAL" in this
document are to be interpreted as described in RFC 2119 [34].
        \paragraph{}
An implementation is not compliant if it fails to satisfy one or more
of the MUST or REQUIRED level requirements for the protocols it
implements. An implementation that satisfies all the MUST
level requirements but not all the SHOULD level requirements for its
protocols is said to be "conditionally compliant"; one that satisfies
all the MUST or REQUIRED level and all the SHOULD level requirements
for its protocols is said to be "unconditionally compliant";
        \paragraph{}
The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT",
"SHOULD", "SHOULD NOT", "RECOMMENDED", "MAY", and "OPTIONAL" in this
document are to be interpreted as described in RFC 2119 [34].

    \section{Terminology}
        \paragraph{}
This specification uses a number of terms to refer to the roles
played by participants in, and objects of, the BEEP communication.
        \paragraph{connection}
A transport layer virtual circuit established between two programs
in order to establish a communication.
        \paragraph{login IDs}
A combination of login and password.
        \paragraph{message}
The basic unit of BEEP communication, consisting of a structured
sequence of octets matching the syntax defined in section 4 and
transmitted via the previously established connection.
        \paragraph{request}
A BEEP request message, as defined in section 5.
        \paragraph{response}
A BEEP response message, as defined in section 6.
        \paragraph{resource}
A network data object or service that can be identified by a URI,
as defined in section 3.2. Resources may be available in multiple
representations (e.g. multiple languages, data formats, size, and
resolutions) or vary in other ways.
        \paragraph{entity}
The information transferred as the payload of a request or
response. An entity consists of meta-information in the form of
entity-header fields and content in the form of an entity-body, as
described in section 7.
        \paragraph{representation}
An entity included with a response that is subject to content
negotiation, as described in section 12. There may exist multiple
representations associated with a particular response status.
        \paragraph{content negotiation}
The mechanism for selecting the appropriate representation when
servicing a request, as described in section 12. The
representation of entities in any response can be negotiated
(including error responses).
        \paragraph{client}
A program that establishes connections for the purpose of sending
requests.
        \paragraph{server}
An application program that accepts connections in order to
service requests by sending back responses. Any given program may
be capable of being both a client and a server; our use of these
terms refers only to the role being performed by the program for a
particular connection, rather than to the program's capabilities
in general. Likewise, any server may act as an origin server,
proxy, gateway, or tunnel, switching behavior based on the nature
of each request.
        \paragraph{origin server}
The server on which a given resource resides or is to be created.
        \paragraph{semantically transparent}
A cache behaves in a "semantically transparent" manner, with
respect to a particular response, when its use affects neither the
requesting client nor the origin server, except to improve
performance. When a cache is semantically transparent, the client
receives exactly the same response (except for hop-by-hop headers)
that it would have received had its request been handled directly
by the origin server.
        \paragraph{upstream/downstream}
Upstream and downstream describe the flow of a message: all
messages flow from upstream to downstream.

    \section{Overall Operation}
        \paragraph{}
BEEP is a request/response protocol. The client send a request to the
server and the server answer with a response. All the messages
(requests and responses) go through a connection between the server
and the client. The connection MUST be established before any request
other than those using the CONNECT method occurs.
The request is composed of a method, an entity and the protocol
version.
        \paragraph{}
The response is composed of a status-line, response-headers and in
some cases an entity.


    \clearpage
\chapter{Notational Conventions and Generic Grammar : Basic Rules}
    \paragraph{}
The following rules are used throughout this specification to
describe basic parsing constructs. The US-ASCII coded character set
is defined by ANSI X3.4-1986 [21].
    \paragraph{}
OCTET          = <any 8-bit sequence of data>
    \paragraph{}
CHAR           = <any US-ASCII character (octets 0 - 127)>
    \paragraph{}
DIGIT          = <any US-ASCII digit "0".."9">
    \paragraph{}
INT            = <basic signed integer type. cf ISO/IEC 9899>
    \paragraph{}
LONG INT       = <long signed integer type. cf ISO/IEC 9899>
    \paragraph{}
FLOAT          = <floating-point type. cf IEEE 754>
    \paragraph{}
SP             = <US-ASCII SP, space (32)>
    \paragraph{}
CR             = <US-ASCII CR, carriage return (13)>
    \paragraph{}
LF             = <US-ASCII LF, linefeed (10)>
    \paragraph{}
LWS            = <US-ASCII LWS, linear white space (9)>
    \paragraph{}
<">            = <US-ASCII double-quote mark (34)>


    \clearpage
\chapter{Protocol Parameters}
    \section{Date/Time Formats}
        \paragraph{Full Date}
This application allows only one full date format :
    24-11-2014 14:41:12 GMT
This is a format from the RFC 3339.
        \paragraph{Delta Seconds}
Delta Seconds represents a difference between server's starting
time and current time.
    \section{Character Sets}
        \paragraph{}
BEEP uses the same definition of the term "character set" as that
described for BEEP :
The term "character set" is used in this document to refer to a
method used with one or more tables to convert a sequence of octets
into a sequence of characters. Note that unconditional conversion in
the other direction is not required, in that not all characters may
be available in a given character set and a character set may provide
more than one sequence of octets to represent a particular character.
This definition is intended to allow various kinds of character
encoding, from simple single-table mappings such as US-ASCII to
complex table switching methods such as those that use ISO-2022's
techniques. However, the definition associated with a BEEP character
set name MUST fully specify the mapping to be performed from octets
to characters. In particular, use of external profiling information
to determine the exact mapping is not permitted.


    \clearpage
\chapter{BEEP Message}
    \section{Message Types}
        \paragraph{}
BEEP messages consist of requests from client to server and responses
from server to client.
        \paragraph{}
Request (section 5) and Response (section 6) messages use a generic
message format for transferring entities (the payload of the
message). Field names are case-sensitive. The field value MAY be
preceded by any amount of LWS, though a single SP is preferred.

    \section{Message Headers}
        \paragraph{}
Headers are only response-headers. Headers end with a single CR.
Each header field consists of a name followed by a colon (":") and
the field value. Header fields ends with a semi-colon (";"). The
headers are case-sensitive.

    \section{Message Body}
        \paragraph{}
The message-body is used to transfer informations associated with a
request or a response. The message body ends with a double CR.

    \section{Message Length}
        \paragraph{}
The message-length is the length of the headers if there is any plus
the length of the message-body (cf entity section (8) for the length
of an entity).


    \clearpage
\chapter{Request}
    \section{Request-Line}
        \paragraph{}
The Request-Line begins with a method keyword, followed by the entity
on which is applied this method.
        \paragraph{}
The Method keyword indicates the method to be used on the resource
identified by the Request-entity. The method is case-sensitive.
        \paragraph{}
Method         = "GET"                    cf. section 9.1
        \paragraph{}
                | "PUT"                    cf. section 9.2
        \paragraph{}
                | "DELETE"                 cf. section 9.3
        \paragraph{}
                | "CONNECT"                cf. section 9.4


    \clearpage
\chapter{Response}
    \paragraph{}
After receiving and interpreting a request message, a server responds
with an BEEP response message.
    \section{Status-Line}
        \paragraph{}
The first line of a Response message is the Status-Line, consisting
of the protocol version followed by a numeric status code and its
associated textual phrase, with each element separated by SP
characters. No CR is allowed except in the final CR sequence.
        \paragraph{}
Status-Line = BEEP-Version SP Status-Code SP Reason-Phrase CR
        \paragraph{Status Code and Reason Phrase}
The Status-Code element is a signed 1-digit integer. This is the
result code of the attempt to understand and satisfy the request.
These codes are fully defined in section 10. The Reason-Phrase is
intended to give a short textual description of the Status-Code. The
Status-Code is intended for use by automate and the Reason-Phrase is
intended for the human user. The client is not required to examine or
display the Reason-Phrase.
        \paragraph{Status-line length}
The CHAR length of the status-line is described below :
|---------------|----|-----------------|----|
| {Status Code} | SP | {Reason Phrase} | CR |
|---------------|----|-----------------|----|
|       2       |  1 |        12       |  1 |
|---------------|----|-----------------|----|

(total CHAR length) = 16
    \section{Response Header Fields}
        \paragraph{}
The CHAR length of the response header line is described below :
|----------------|---|----|------------------|---|-»
| Content-length | : | SP | {Content-length} | ; |-»
|----------------|---|----|------------------|---|-»
|       14       | 1 |  1 |        15        | 1 |-»
|----------------|---|----|------------------|---|-»

«-|--------------|---|----|----------------|---|----|
«-| Content-type | : | SP | {Content-type} | ; | CR |
«-|--------------|---|----|----------------|---|----|
«-|      12      | 1 |  1 |       16       | 1 |  1 |
«-|--------------|---|----|----------------|---|----|

(total CHAR length) = 64
        \paragraph{Content-Length}
It's the response body length.
        \paragraph{Content-Type}
It's the type of entity of the body (cf section 7).


    \clearpage
\chapter{Entity}
    \section{Type}
        \paragraph{}
Entity used by BEEP are composed of basic C vars.
        \paragraph{Object bid}
|----------|----------|------------|-------------|-----------|-»
|    ID    |   Name   | Base Price | Description | Vendor ID |-»
|----------|----------|------------|-------------|-----------|-»
| LONG INT | CHAR[96] |    FLOAT   |  CHAR[320]  |  LONG INT |-»
|----------|----------|------------|-------------|-----------|-»

«-|------------|----------|----------|-------------------|-»
«-| Start Time | End Time |  Adress  | Current Bid Price |-»
«-|------------|----------|----------|-------------------|-»
«-|  LONG INT  | LONG INT | CHAR[96] |       FLOAT       |-»
«-|------------|----------|----------|-------------------|-»

«-|----------------------|
«-| Current Bid Buyer ID |
«-|----------------------|
«-|       LONG INT       |
«-|----------------------|
        \paragraph{User account}
|------|----------|----------|-----------|----------|----------|
| Type |    ID    |   Name   |  Lastname |  Adress  |   Mail   |
|------|----------|----------|-----------|----------|----------|
| CHAR | LONG INT | CHAR[75] |  CHAR[64] | CHAR[96] | CHAR[80] |
|------|----------|----------|-----------|----------|----------|
    \section{Entity Length}
        \paragraph{Object bid}
An object bid is (in OCTET)
4 + 96 + 4 + 320 + 4 + 4 + 96 + 4 + 4 = 536
        \paragraph{User account}
An user account is (in OCTET)
1 + 4 + 75 + 64 + 96 + 80 = 320


    \clearpage
\chapter{Connections}
    \section{Persistent Connections}
        \paragraph{Purpose}
The purpose of the persistent connection is for the client to connect
only once. That way it will reduce the number CONNECT requests, and
clients don't have to send headers with their credentials for each request
they made.
        \paragraph{Overall Operation}
The client send a request using the CONNECT method with its login and
password, if there is any, or a PUT request to create a user account.
In the first case, CONNECT is used and the pair ID/password is correct.
After that, the client is allowed to use the command to add, delete or
bid for an object or to obtain the objects's list.
If not, the client SHOULD use an other ID/password couple to connect
or use the PUT request to create an account.
    \section{Message Transmission Requirements}
        \paragraph{}
One (or more) network connection is required if the server and clients
don't run on the same system.
BEEP also require the choosen connexion port availability.
        \paragraph{Client Behavior if Server Prematurely Closes Connection}
If the server closes the connection, the client SHOULD shut down either.
After that the client CAN restart its use.


    \clearpage
\chapter{Method Definitions}
    \section{GET}
        \paragraph{}
The GET method enable the client to ask the server to send back an entity.
This method requires X parameters and have the following length :
|-----|----|----------|---|----|
| GET | SP | {OBJECT} | ; | CR |
|-----|----|----------|---|----|
|  3  |  1 | {OBJECT} | 1 |  1 |
|-----|----|----------|---|----|
        \paragraph{}
(total CHAR length) = 6
+ ({Object} length)
    \section{PUT}
        \paragraph{}
The client requests the server to store the a requested entity sent
in the core of the request.
This method requires X parameters and have the following length :
|-----|----|----------|---|----|
| PUT | SP | {OBJECT} | ; | CR |
|-----|----|----------|---|----|
|  3  |  1 | {OBJECT} | 1 |  1 |
|-----|----|----------|---|----|
        \paragraph{}
(total CHAR length) = 6
+ ({Object} length)
    \section{DELETE}
        \paragraph{}
The client requests the server to delete the requested entity from
his database. For the entity types, cf section 7. To delete an
object or a user account, the client must be authenticed as the
object's creator or an administrator.
This method requires one parameters and have the following length :
|--------|----|----------|---|----|
| DELETE | SP | {OBJECT} | ; | CR |
|--------|----|----------|---|----|
|    6   |  1 | {OBJECT} | 1 |  1 |
|--------|----|----------|---|----|
        \paragraph{}
(total CHAR length) = 9
+ ({Object} length)
    \section{CONNECT}
        \paragraph{}
The CONNECT method is used by the client to establish a permanent
connection with the server.
This method requires two parameters and have the following length :
|---------|----|---------|---|------------|---|----|
| CONNECT | SP | {LOGIN} | ; | {PASSWORD} | ; | CR |
|---------|----|---------|---|------------|---|----|
|    7    |  1 |    27   | 1 |     26     | 1 |  1 |
|---------|----|---------|---|------------|---|----|
        \paragraph{}
(total CHAR length) = 64


    \clearpage
\chapter{Status Code Definitions}
        \paragraph{}
The status code is the first part of the server answer for a request.
    \section{Positive (X)}
        \paragraph{0 OK}
The request has succeeded. The information returned with the
response is dependent on the method used in the request, for
example :
    | GET      an entity corresponding to the requested resource
    |          is sent in the response;
    |
    | PUT      an entity-header with the return status;
    |
    | DELETE   an entity-header with the return status;
    |
    | CONNECT  an entity-header with the return status;
        \paragraph{1 Created}
Result of a successful account or object bid creation.
    \section{Negative (-X)}
        \paragraph{-1 Bad Request}
The request could not be understood by the server due to malformed
syntax. The client SHOULD NOT repeat the request without
modifications.
        \paragraph{-2 Not Created}
The request could not be understood by the server due to a problem
with the ressource designed by the request.
Result of a failed account or object bid creation.
        \paragraph{-3 Internal Server Error}
The server encountered an unexpected condition which prevented it
from fulfilling the request.
Result of an unknown, unpredictable or internal (core) server error.
        \paragraph{-4 Conflict}
Result of a concurrent object bid read and write access between more
than one user and/or administrator.
        \paragraph{-5 Forbidden}
The server understood the request, but is refusing to fulfill it.
Authorization will not help and the request SHOULD NOT be repeated.
Result of giving invalid connection ids, or call a method which needs
rights but without them.


    \clearpage
\chapter{Access Authentication}
        \paragraph{}
It require to use the CONNECT method with the user's login IDs.
The server sends back a response message composed of the status line.


    \clearpage
\chapter{Security Considerations}
        \paragraph{}
At the moment, no encryption module is in use, all the content is
sent clearly through the Internet. Please be careful while using this
version of the protocol. You MUST consider these severe security
issues !
    \section{Personal Information}
        \paragraph{}
Your login, your password, and any informations you could send CAN be
viewed by anyone who is watching your communications under this
protocol.
    \section{Privacy Issues Connected to Accept Headers}
        \paragraph{}
..............
    \section{Authentication Credentials and Idle Clients}
        \paragraph{}
At the moment, all your credentials pass through one or more networks
without protections. Anyone can take them from the BEEP connect
request and/or from the answer of a GET request of user informations.


    \clearpage
\chapter{Acknowledgments}
        \paragraph{}
This specification makes heavy use of the generic definitions as they
can be seen in the RFC 2616. We would like to thanks the author to
allow us to use those definitions.
        \paragraph{}
Moreover, we want to thanks our professors P. Torguet and A. Aoun for
all their teaching and advising.


    \clearpage
\chapter{References}
        \paragraph{}
   [1] R. Fielding, UC Irvine, J. Gettys, Compaq/W3C, J. Mogul, Compaq,
       H. Frystyk, W3C/MIT, L. Masinter, Xerox, P. Leach, Microsoft,
       T. Berners-Lee, W3C/MIT, "Hypertext Transfer Protocol", RFC 2616,
       June 1999.


    \clearpage
\chapter{Full Copyright Statement}
        \paragraph{}
For the general definitions and some help in the structuration of our
rfc, we used the rfc 2616 (HTTP/1.1), as it is authorized by the
copyright statement below.
        \paragraph{}
Copyright (C) The Internet Society (1999).  All Rights Reserved.
        \paragraph{}
This document and translations of it may be copied and furnished to
others, and derivative works that comment on or otherwise explain it
or assist in its implementation may be prepared, copied, published
and distributed, in whole or in part, without restriction of any
kind, provided that the above copyright notice and this paragraph are
included on all such copies and derivative works.  However, this
document itself may not be modified in any way, such as by removing
the copyright notice or references to the Internet Society or other
Internet organizations, except as needed for the purpose of
developing Internet standards in which case the procedures for
copyrights defined in the Internet Standards process must be
followed, or as required to translate it into languages other than
English.
        \paragraph{}
The limited permissions granted above are perpetual and will not be
revoked by the Internet Society or its successors or assigns.
        \paragraph{}
This document and the information contained herein is provided on an
"AS IS" basis and THE INTERNET SOCIETY AND THE INTERNET ENGINEERING
TASK FORCE DISCLAIMS ALL WARRANTIES, EXPRESS OR IMPLIED, INCLUDING
BUT NOT LIMITED TO ANY WARRANTY THAT THE USE OF THE INFORMATION
HEREIN WILL NOT INFRINGE ANY RIGHTS OR ANY IMPLIED WARRANTIES OF
MERCHANTABILITY OR FITNESS FOR A PARTICULAR PURPOSE.
